\documentclass[solution,addpoints,12pt]{exam}
\printanswers
\usepackage{amsmath,amssymb}

\newcommand{\RP}{\ensuremath{\mathsf{RP}}}
\newcommand{\expect}[1]{\ensuremath{\mathbb{E}[#1]}}
\newcommand{\dx}{\mathrm{d}x}


\begin{document}

\hrule
\vspace{3mm}
\noindent 
{\sf IITM-CS4410 : Topics in Algoritmic Combinatorics and Grapth Theory  \hfill Given on: Jan 29, 17:00}
\vspace{3mm}\\
\noindent 
{\sf Problem Set \#1 \hfill Due on : Feb 13 , 23:55 }
{\sf ~\hfill Evaluation due: Feb 25, 17:00}
\vspace{3mm}
\hrule
{\small
\begin{itemize}
\item Turn in your solutions electronically at the institute moodle (courses.iitm.ac.in) page. Those who are not familiar with latex, may submit handwritten solutions to the instructor or TAs. 
  Use LaTeX.
\item  You are expected to obtain the solutions independently.    
\item Any form of plagiarism will be reported to the Institute Disciplinary committee
\item  You are discouraged from using any source (internet, textbooks etc) for obtaining the solution. In case referred to, it should be indicated.  
\item Kindly use this latex file to type in your solutions. % by un-commenting the lines begin(solution) end(solution).
\end{itemize}}
\hrule
\vspace{3mm}
\begin{questions}

%\begin{solution}
%\end{solution}

\question[6]  Recall the definition of a cut and a bond in a graph. Show that a cut in a connected graph $G$ is a bond if and only if the corresponding bipartition of $V(G)$ are connected in $G$. 
 %\begin{solution}
%\end{solution} 

\question[6] Show that the cycle space of a graph is spanned by its induced cycles.  
 %\begin{solution}
%\end{solution}
\question[8] Let $G$ be a connected graph and $T$ be a spanning tree of $G$. For an edge $e\in G\setminus T$, let $C_e$ be the fundamental cycle of $e$ with respect to $T$ and for an edge $f\in T$ let $D_f$ denote the fundamental cut of $f$ with respect to $T$. Show that $e\in D_f \iff f \in C_e$  
 %\begin{solution}
%\end{solution} 
\question[10] Suppose $k\ge 2$ and $G$ be a $k$-connected graph. Show that for any $S\subseteq V$ with $|S| = k$, $G$ has a cycle containing all of the vertices in $S$. 
 
%\begin{solution}
%\end{solution}



\end{questions}
\end{document}
